\documentclass{article}
\usepackage{CJK}
\begin{document}
\begin{CJK*}{GBK}{song}
  
\section{Definition of IC }

There is no universally accepted definition of IC in the literature. Following Edvinsson and Malone (1997, p. 44), IC is 'the possession of knowledge, applied experience, organisational technology, customer relationships and professional skills that provide the firm with a competitive edge in the market'. On the other hand, Bontis et al. (1999) stressed the importance of IC flows and defined IC as 'the collection of intangible resources and their flows'. This definition implies the dynamic nature of IC and its development through time. Lev (2001, p. 5) says that IC is 'a claim to future benefits that does not have a physical or financial embodiment'.

\subsection{Three categories of IC}
There is a widely accepted three-category IC classification into (i) human, (ii) structural,and (iii) customer or relationship capital (Saint-Onge, 1996; Edvinsson and Malone, 1997;Sveiby, 1997; Roos et al., 1997; Stewart, 1999). First, human capital is represented by the intangible assets embodied by individuals. Roos et al. (1997, p. 32) argued that peoplegenerate capital through competence (represented by skills and education), their attitude (which covers the behaviour of employees towards their work) and their intellectual agility (represented by innovativeness and openness to changes). Second, structural capital is owned by the firm (Stewart, 1999, p. 109). Following Bontis (1996), it includes routines and structures. Stewart (1999, p. 109) states that culture is also an extensive and valuable element of structural capital. Structural capital is constituted by
ARTICLE IN PRESS H.N. Rudezˇ, T. Mihalicˇ / Hospitality Management 26 (2007) 188C199 189 management philosophy, culture, business processes and information technology in the hotel industry (Nemec Rudezˇ , 2004). Third, customer capital is owned by every firm that has customers (Stewart, 1999, p. 143). It is constituted by customer satisfaction and loyalty, image and brand, and direct distribution channels (Nemec Rudezˇ , 2004). Customer capital can be broadened to relationship capital, which also includes relationships with other subjects such as business partners, tourism promotion organisations, government, local community, competitors, creditors, special interest groups, the media and the public.

\section{考虑最小成本的情况}

\section{参数为确定性的情况}


已知有N种知识资产, 每种资产有M种获得方式，用$n_{ij}$表示以第j种方式获得的第j种资产， 价格为$P_{ij}$。对于一种知识资产，企业有最小需求$\sum_jn_{ij}\ge b_i$。由于知识资产的特殊性，有的资产的供应量没有上界，有的资产的供应量是有限制的。对于有限制的资产应满足$\sum_jn_{ij} \l
e s_i$。此外，投入的总成本应小于公司预算，每一种资产的投入额也应小于相应的数额。因此模型如下：
\begin{eqnarray*}
 &min& c =  \sum_i\sum_jp_{ij}n_{ij} \\ & s.t& \sum_jn_{ij}\ge b_i \\ && \sum_jn_{ij} \le s_i \\ && \sum_i\sum_jp_{ij}n_{ij} \le T \\ && \sum_jp_{ij}n_{ij} \le t_j \\ && p_{ij}, n_{ij} \ge 0 \\ && n_{ij}\in Z^+ 
\end{eqnarray*}

\section{参数为不确定的情况}
\section{考虑最大收益的情况}
记$r_{i}$为某项资产的收益
\begin{eqnarray*}
 &max& R = \sum_i\sum_jr_{i}n_{ij} - \sum_i\sum_jp_{ij}n_{ij} \\ & s.t& \sum_jn_{ij}\ge b_i \\ && \sum_jn_{ij} \le s_i \\ && \sum_i\sum_jp_{ij}n_{ij} \le T \\ && \sum_jp_{ij}n_{ij} \le t_j \\ && p_{ij}, n_{ij}, r_i \ge 0 \\ && n_{ij}\in Z^+ 
\end{eqnarray*}

\section{收益的确定}

\begin{itemize}
\item 一般资产。收益可以根据已有的数据预测。
\item 替代资产。该项资产在本生产周期内不是必需的，但是可以提供某种权利使得在外界环境发生变化时企业活动可以正常开展。令它的收益为其期权价值。
\item （保险？？）资产。能够为企业减少损失，收益为它的精算价值。
\end{itemize}

\end{CJK*}
\end{document}

%%% Local Variables 
%%% mode: latex
%%% TeX-master: t
%%% End: 
