\documentclass{article}

\begin{document}
\title {A stochastic programming model for knowledge asset management under knowledge grid circumstance}
\maketitle
\begin{abstract}
  This paper intends to model knowledge asset management issues of manufacturing enterprises using multi-stage stochastic programming framework. Under knowledge grid circumstance, these assets are allowed to have price so they can trade and exchange freely. The object of this model is to minimize accumulative expected discounted value of knowledge assets investment while meet manufacturing needs at some favorable level. Uncertainties include demand and supply quantity, price, which come from service market. Also constraints are taking into accounts such as manufacturing capacity, time of delivery, priority of buyers and substitutability between different assets. Decisions adapt to available information at the time they are made.
\end{abstract}

\section{Introduction}
\label{sec:introduction}

 More and more companies are realizing knowledge serves as the most important assets in a company. The products contains more knowledge than ever and the trends will keep going whith intensive competences. knowledge service as a means to stimulate knowledge sharing and team collaboration has proved its value. With knowledge service, pepole from distributated location .

knowledge service combines knowledge and service to provide an integrated architect for solving task. The most salient characteristics of knowledge service are that it provide not only service but knowledge simutaniously. 

The main purpose of knowledge service is to provide knowledge application and creation based on the capabilty of searching, organizing, analysing, and applying information and knowledge. User's context is also accounted along with the user's issues. The knowledge is not provide directly to user but through processing and reforming so knowledge service can supply more accurate and cheap service. 
Knoeledge service has a few characteristics which enable it more suitable for trade than knowledge asset.
\begin{itemize}
\item Knowledge assets are hard to price because of their high investment but easier to copy and distribute.
\item 
\end{itemize}

knowlege grid  boost
\end{document}
